Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-17 manuscript/manuscript.tex
Changes in manuscript and speed-comparison figure

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows us to generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions and classes can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

@@

\todo{speed comparison between homogeneous and variable density}

@@

On the other hand, the accuracy of the method is exclusively controlled by the value assigned to the distance-size ratio $D$, which cannot be easily related to the error of the approximation.
In order to solve this, \citet{Uieda2016} compared the numerical computation with the analytical solution for a spherical shell with homogeneous density.

>>>>

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows to generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions and classes can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

@@

@@

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous and variable density at different heights (see Figure \ref{fig:speed-comparison}).
Firstly, we can see that both codes take more time to compute the gravity field for lower heights due to the increased divisions of the tesseroid in such cases.
Secondly, we can see that the homogeneous density code is up to twice faster than the new variable density algorithm, however the later is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation times for a single tesseroid model with homogeneous and variable density at different heights.}
\label{fig:speed-comparison}
\end{figure}

On the other hand, the accuracy of the method is exclusively controlled by the value assigned to the distance-size ratio $D$, which cannot be easily related to the error of the approximation.
In order to overcome this, \citet{Uieda2016} compared the numerical computation with the analytical solution for a spherical shell with homogeneous density.
